### 2018-11-13 ms/ms_prosop.tex
updated readme and document

\subsubsection*{Data Availability}
\small{
	fMRI results maps are available on \\
	\href{https://neurovault.org/collections/4017/}{neurovault.org/collections/4017}  \\
	Code to reproduce the results and figures, as well as to recreate this manuscript, can be found on  \\
	\href{https://doi.org/10.5281/zenodo.1485911}{doi.org/10.5281/zenodo.1485911}.}

>>>>

\subsubsection*{Data Availability}
\small{
	fMRI result maps are available on NeuroVault \\
	\href{https://neurovault.org/collections/4017/}{\includegraphics[height=0.4cm]{./neuro-4017-red.png}}  \\
	Code to reproduce the results and figures, as well as to recreate this manuscript, can be found on GitHub/zenodo \\
	\href{https://doi.org/10.5281/zenodo.1486122}{\includegraphics[height=0.4cm]{./zenodo-1486122-blue.png}}
